---
title: "Exploratory Data Analysis and Modeling"
author: "Veronica Weiss"
date: "4/6/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(corrplot)
library(caret)
library(OneR)
library(mlbench)
library(e1071)
```

#Exploratory Data Analysis 


```{r}
phish <- read.csv('/Users/vee/Downloads/TrainingDataset.csv')
```

We begin Exploratory Data Analysis by seeing the correlations between the variables.
#Show half of the plot
#Box plots to show the different levels of 0 and 1 
#Tapply (quantitative, categorical, function)
```{r}
cor.p <- cor(phish)
cor.p[]
cor.p
corrplot(cor.p, type = "upper", tl.pos = "td",
         method = "circle", tl.cex = 0.5, tl.col = 'black',
         order = "hclust", diag = FALSE)
```

It appears that a relationship between domain_registration length and the following variables: URL_Length, Result, Request_URL. Based on the correlation, Domain_registration_length has the strongest relationship with Request_URL. 

It appears that Redirect has a relationship between DNSRecord, Having_IP_Address, Abnormal_URL, HTTPS_token, Shortnining_Service, and double_slash_redirecting. The strongest relationship for Redirect seems to be double_slash_redirecting in the negative direction, but the other 4 variables previously listed are also somewhat strongly negatively related to Redirect. 

It appears that links_pointing_to_page has a strong negative relationship with having_IP_address and DNSRecord.

The following are strong positive correlations in this dataset:
RightClick and iFrame
RightClick and Port
RightClick and Submitting_to_Email
RightClick and on_mouseover
RightClick and Favicon
RightClick and Pop up Window
SSLfinal_State and Result
URL_of_Anchor and Result 
URL_Length and SFH

The following are strong negative correlations in this dataset:
Request_URL and Domain_registration_length
Abnormal_URL and Redirect
HTTPs_Token and Redirect
Shortning_Service and Redirect
double_slash_redirecting and Redirect


Variables with one or more positive otable correlation are: Shortning_Service, HTTPS_Token, Abnormal_URL, DNSRecord, Favicon, on_mouseover, Submitting_to_email, port, iframe, RightClick,SSLfinal_State, URL_of_Anchor, Prefix_Suffix, URL_Length

*~~*SO LET'S VISUALIZE**~~*
  colors = c("#CD1658", "#4000E6")


Graphs to make:
Waffle chart 
```{r}
ggplot(phish, aes(x = Result, color = Result)) + geom_histogram(fill = "#3ECBC4") + ggtitle("Histogram of Result")
```

The dataset has identified more websites to be phishing than not phishing. 

Bar plot 
Bar plot with a grouping 
Box plot  (used with arrange)
Boxen plot 

#Splitting the Data into Train and Test Sets

60% of the data will be in the training set. 

```{r}
trainSet <- createDataPartition(phish$Result, p=.6)[[1]]
phish.train <- phish[trainSet,]
phish.test <- phish[-trainSet,]
```

#Modeling
MODELS TO TRY:
Naive Bayes
RIPPER
XGboost
Light GBM 

We can use Naive Bayes and RIPPER (rRepeated Incremental Pruning to Produce Error Reduction). Each model will have a section for feature extraction, modeling, and evaluation. Then after we preform all those steps, we will enter the deployment phase by avowing which model is the most optimal.


##Modeling for Naive Bayes

```{r}
phish.train$Result <- as.factor(phish.train$Result)
phish.test$Result <- as.factor(phish.test$Result)
```

```{r}
phish.nb.model <- naiveBayes(Result ~ ., data = phish.train)
phish.nb.pred <- predict(phish.nb.model, phish.test)
  
eval_model(phish.nb.pred, phish.test)
```

Out of the box Naive Bayes: 71% accuracy.

##Feature Extraction for Naive Bayes
```{r}
control <- rfeControl(functions = nbFuncs)
rfe <- rfe(phish.train[,1:30], as.factor(phish.train[,31]), sizes = c(1:30), rfeControl = control)
```

```{r}
rfe
```
